Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-23 manuscript/manuscript.Rmd
added escapement-msy tuning fig

@@

@@

```{r}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, 
                      warning = FALSE, fig.height=5, fig.width=7.5)
msy <- read_csv("../data/msy.csv.gz")
ppo <- read_csv("../data/PPO250.csv.gz")
escapement <- read_csv("../data/escapement.csv.gz", show_col_types = FALSE)

# rename some columns for figure purposes:
colnames(msy) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z')
colnames(ppo) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z') 
colnames(escapement) <- c('t', 'rep', 'esc_level', 'reward', 'X', 'Y', 'Z') 
opt_escapement <- escapement |> filter(esc_level == 0.62)
head(opt_escapement)

>>>>

```{r}
# Collect data (outsource to separate R script later TBD)
msy <- read_csv("../data/msy.csv.gz")
ppo <- read_csv("../data/PPO250.csv.gz")
escapement <- read_csv("../data/escapement.csv.gz", show_col_types = FALSE)

# rename some columns for figure purposes:
colnames(msy) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z')
colnames(ppo) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z') 
colnames(escapement) <- c('t', 'rep', 'esc_level', 'reward', 'X', 'Y', 'Z') 
opt_escapement <- escapement |> filter(esc_level == 0.62)

@@

# Fishery management figures

```{r escapement_msy, fig.cap="TBD.", out.width = "6.5in"}
library(patchwork)
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

esc_rewards <- escapement |>
  group_by(esc_level, rep) |>
  filter(t == max(t)) |> 
  group_by(esc_level) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

rmsy <- msy_rewards |>
  ggplot(aes(action, mean_reward, 
             ymin = mean_reward - 2*sd,
             ymax=mean_reward+2*sd)) +
  geom_point() + geom_ribbon(alpha=0.4) +
  labs(y = "episode reward", x = "constant mortality") +
  theme(aspect.ratio = 1/1)

resc <- esc_rewards |>
  ggplot(aes(esc_level, mean_reward, 
             ymin = mean_reward - 2*sd,
             ymax=mean_reward+2*sd)) +
  geom_point() + geom_ribbon(alpha=0.4) +
  labs(y = "episode reward", x = "constant escapement") +
  theme(aspect.ratio = 1/1)

(rmsy | resc)
```

@@
